---
title: "Simple document"
output: html_document
---

```{r}
library(tidyverse)
```

I'm an R Markdown document! Commit example!

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
To round your mean to 2 digits do:
`round(mean(samp), 2)`

# Section 3

This is going to make a plot! With a dataframe, you can make a scatter plot with `ggplot`
The way to create a code chunk hit command+option+I
```{r}
plot_df =
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )
```

# My Own Code Chunk
```{r learning assessment_1}
library(tidyverse)

la_df = 
  la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.

Changing again!
```



